Dependently Typed Languages in Statix

### 2022-11-02 paper-evcs/paper.tex
Work
Add orcids

\author{Jonathan Brouwer}{Delft University of Technology, The Netherlands \and \url{http://jonathanb.nl}}{j.t.brouwer@student.tudelft.nl}{}{}

\author{Jesper Cockx}{Delft University of Technology, The Netherlands \and \url{http://jesper.sikanda.be}}{j.g.h.cockx@tudelft.nl}{}{}

\author{Aron Zwaan}{Delft University of Technology, The Netherlands \and \url{http://aronzwaan.github.io}}{a.s.zwaan@tudelft.nl}{}{}

@@

\begin{lstlisting}
let f = \T: Type. \x: T. x;
f (_: Type -> Type) (\x: Type. x)
\end{lstlisting}
The AST of this program in Aterm format would be:
\begin{lstlisting}
Let(
  "f", 
  FnConstruct("T", Type(), FnConstruct("x", Var("T"), Var("x"))),
  FnDestruct(
	FnDestruct(Var("f"), FnConstruct("_", Type(), Type())),
	FnConstruct("x", Type(), Var("x"))
  )
)
\end{lstlisting}

>>>>

\author{Jonathan Brouwer}{Delft University of Technology, The Netherlands \and \url{http://jonathanb.nl}}{j.t.brouwer@student.tudelft.nl}{https://orcid.org/0000-0002-2469-548X}{}

\author{Jesper Cockx}{Delft University of Technology, The Netherlands \and \url{http://jesper.sikanda.be}}{j.g.h.cockx@tudelft.nl}{https://orcid.org/0000-0003-3862-4073}{}

\author{Aron Zwaan}{Delft University of Technology, The Netherlands \and \url{http://aronzwaan.github.io}}{a.s.zwaan@tudelft.nl}{https://orcid.org/0000-0002-1818-4245}{}

@@

\begin{lstlisting}
let f = \T: Type. \x: T. x;
f (_: Type -> Type) (\x: Type. x)
\end{lstlisting}
The AST of this program in Aterm format\cite{aterm} would be:
\begin{lstlisting}
Let(
  "f", 
  FnConstruct("T", Type(), FnConstruct("x", Var("T"), Var("x"))),
  FnDestruct(
	FnDestruct(Var("f"), FnConstruct("_", Type(), Type())),
	FnConstruct("x", Type(), Var("x"))
  )
)
\end{lstlisting}
